%=====================================================
\begin{abstract}
%=====================================================
We study the security of Quick UDP Internet Connections
(QUIC for short) -- an experimental transport layer
network protocol recently developed by Google.
Lychev et al.~\cite{LJBN15:QUIC}, show that QUIC is secure
in their security model which is called QACCE.
However, QUIC has vulnerabilities against the attacks~\cite{LJBN15:QUIC}
which increase server loads and their security model does not cover these attacks.
QUIC should prevent these attacks because these attacks enable an adversary
to do Distributed Denial of Service (DDoS) attacks.
To cover these security concerns, we propose a new security model,
extending server-only authenticated and channel
confidentiality establishment (SACCE), so that
authentication and channel confidentiality can be
evaluated including abbreviated handshake sessions.
Our security model is stronger than QACCE to cover the security concerns.
We then show that the original QUIC does not satisfy our security
model.
We also propose a new scheme to solve the security concerns
and enhance the performance.
There are three advantages in our proposed scheme.
First, our proposed scheme solve the security concerns which
the original QUIC has.
Second, our proposed scheme does not require Strong Computational Diffie-Hellman~\cite{ABR01}
assumption to satisfy the security model. On the other hand, the original QUIC require
Strong Computational Diffie-Hellman to satisfy QACCE secure.
Third, our proposed scheme reduce a number of interactions from four
to two.
\end{abstract}