%=====================================================
\section{``Resumable" Server-only Authenticated and Confidential Channel Establishment (RSACCE)} \label{sec:rsacce}
%=====================================================
We consider the security of QUIC and its variants.
Our abstract model to capture the cryptographic core
of them is a server-only authenticated and confidential
channel establishment (SACCE) protocol~\cite{KPW13:SACCE},
the server-only authentication version of an ACCE
protocol~\cite{JKSS12:ACCE}.
In our SACCE protocol, a client initiates an instance
of the protocol and a server always sends the last
message of the instance.
We then extend the security notion of
SACCE~\cite{KPW13:SACCE} to the notion of
\textit{resumable} SACCE (RSACCE).
The main difference between SACCE and RSACCE is that this model treats
abbreviate handshakes.
As mentioned above, an abbreviate handshake takes
advantage of a prior established full handshake session
between the same client and server.
To treat abbreviate handshakes in the server-only
authenticated setting, we should take into account the
attack
\textbf{where an adversarial client fools a
server and impersonates the initial client in an
abbreviate handshake session.}
Depending on the extent of the attack, we define two
security requirements, denoted
\textit{server authentications} and
\textit{channel confidentiality}.
The channel confidentiality implies that, in contrast
to SACCE, an adversary is allowed to submit an
encryption query
\textit{not only to a client but to a server} in an
abbreviate handshake session.
We note that if an adversary can make a handshake with
a server with the same session key in some abbreviate
handshake session, then it can indeed break message
confidentiality of a ciphertext sent by the server.
QACCE also treats abbreviate handshakes.
However, QACCE does not cover the attack because the
adversary is allowed to send encryption query only to
oracles which has matching conversation with intended
partner.
The main differences between QACCE and RSACCE are that
this model (1) ensure the consistency of a client between
1-RTT connections and 0-RTT connections and (2) cover the
security of initial key.
For more details about (2), in this model, the adversary
cannot make a client and server share a different key.
However, in QACCE, the adversary can make a client and
server share a different key because QACCE only consider
the security of forward secure key.

%=====================================================
\subsection{Execution Environment} \label{sec:exec_env_party}
%=====================================================
We basically borrow the notations
from~\cite{JKSS12:ACCE,KPW13:SACCE}.
We denote by $\Client$ and $\Server$ the set of honest
clients and servers, respectively.
We assume for simplicity that each client $\Client$
and server $\Server$ has a \textit{unique} identity
number $c \in \Nset$
\footnote{Since a client has no certified identity,
the numbering is just conceptual.}
and $s \in \Nset$.
For the case we don't need to specify clients or
servers, we also assume that each party
$P \in \Server \cup \Client$ has a \textit{unique}
identity number $p \in \Nset$.
In particular, $\Server$ with identity number $s$ has a unique key pair
$(\pk_s, \sk_s)$, along with a certificate
$\cert_s=(s,\pk_s)_{\text{CA}}$ signed by a certificate
authority CA.
A party $P$ with identity number $p$ maintains a collection of oracles
$\{\pi^p_{i,\ell }\}_{i,\ell}$ where oracle
$\pi^p_{i, \ell}$ models party $P$ executing a single
instance of a protocol in the $\ell$-th abbreviate
handshake session derived from the $i$-th full
handshake session.
When $\ell=0$, $\pi^p_{i,\ell}$ refers to the $i$-th
full handshake session of $P$ with identity number $p$.
The oracle $\pi^p_{i, \ell}$ maintains as internal
state the following variables:

\begin{itemize}
 \item{$\Lambda \in \{\accept, \preaccept, \reject,
 \emptyset\}$, the state of a handshake.}

 \item{$\ik, \key \in \mathcal{K}$, the session key
 where $\mathcal{K}$ is the key space of the protocol.
 $\ik$ is called initial key which calculated with
 ephemeral client's Diffie-Hellman value and static
 server's Diffie-Hellman value, and $\key$ is called
 forward-secure key which calculated with ephemeral
 client's Diffie-Hellman value and ephemeral server's
 Diffie-Hellman value.}

 \item{$\peer$, the intended partner. If $P$ is
 $\Client$ with identity number $c$, then $\pi^c_{i,\ell}$ maintains the
 identity of intended partner $\peer \in \Server$.
 Otherwise (if $P$ is $\Server$), it maintains
 the identity of intended partner $\peer \in \Client$.}

 \item{$b$, the challenge bit chosen uniformly.}

 \item{$\theta$, the cache data. The client and server
 cache the information for the future sessions.}
\end{itemize}
The inner state of each oracle is initialized to
($\Lambda$, $\ik$, $\key$, $\peer$, $\theta$) = ($\emptyset$,
$\emptyset$, $\emptyset$, $\emptyset$, $\emptyset$), where
variable $V=\emptyset$ denotes that variable $V$
is undefined.
On one hand, and $b$ is chosen uniformly and fixed.

The adversary issues the following queries to the
oracles:
\begin{itemize}
 \item {$\Send(\pi^p_{i, \ell}, m)$:
 The adversary can use this query to send message
 $m$ to the oracle $\pi^p_{i, \ell}$.
 The oracle will respond with an outgoing message
 according to the protocol specification and its
 internal state.
 The oracle $\pi^p_{i, \ell}$ replies with $\bot$,
 either (a) if $\ell \geq 1$ and
 $(\theta,\peer) = (\emptyset, \emptyset)$, or (b)
 if $\pi^p_{i,\ell}$ has reached state
 $\Lambda = \accept$.
 Otherwise, it does the following: If the adversary
 asks the first $\Send$-query to oracle
 $\pi^p_{i, \ell}$, then the oracle checks whether
 $m = \top$ consists of a special
 ``initiate client session'' symbol $\top$.
 If so, it responds with the first protocol message.
 If $\ell \geq 1$,
 then $\pi^p_{i,\ell}$ \textit{inherits} variables $(\theta,\peer)$ from
 $\pi^p_{i, k}$ ($k < \ell$) which reaches accept state latest
 (modeling an abbreviate handshake session).
 The adversary can send this returned message to any
 oracle even if this oracle is not intended partner of
 the oracle $\pi^p_{i, \ell}$.}

 \item {$\Reveal(\pi^p_{i,\ell})$:
 The oracle $\pi^p_{i,\ell}$ returns session keys
 $\ik$, $\key$, and cache data $\theta$ to respond this query.
 If $\Reveal(\pi^p_{i,\ell})$ is $\tau$-th query issued by the adversary,
 $\pi^p_{i,\ell}$ is said $\tau$-\textit{revealed}.
 For oracles that are not revealed we define
 $\tau = \infty$.}

 \item {$\Corrupt(P)$:
 If $P$ is $\Client$, then returns $\bot$.
 Otherwise, $P$ is $\Server$ with identity number $s$ and returns long-term
 secret key $\sk_s$ and other secrets which are kept
 for a long time such as static Diffie-Hellman secret
 value.
 If $P$ is $\Server$ and $\Corrupt(P)$ is the
 $\tau$-th query issued by the adversary, $P$ is said
 $\tau$-\textit{corrupted}.
 For parties that are not corrupted we define
 $\tau = \infty$.}

\item {$\Corrupt(\pi^p_{i,\ell})$:
 If $\pi^p_{i,\ell}$ is a client oracle, then returns $\bot$.
 Otherwise, $\pi^p_{i,\ell}$ is a server oracle and returns
 Diffie-Hellman secret value $t_s$ in $\SCFG$.
 If $\pi^p_{i,\ell}$ is a server oracle and $\Corrupt(\pi^p_{i,\ell})$ is the
 $\tau$-th query issued by the adversary, $\pi^p_{i,\ell}$ is said
 $\tau$-\textit{corrupted}.
 For oracles that are not corrupted we define
 $\tau = \infty$.}

 \item {$\Encrypt(\pi^p_{i,\ell}, m_0, m_1, \iv, H)$:
 If $\pi^p_{i,\ell}$ has state
 $\Lambda$ $\not\in$ \\ $\{\preaccept, \accept\}$,
 it returns $\bot$.
 Otherwise, it makes a challenge ciphertext according to
 the procedure in Fig.~\ref{fig:LHAE_rsacce}.}

 \item {$\Decrypt(\pi^p_{i, \ell}, c, \iv, H)$:
 The oracle $\pi^p_{i, \ell}$ replies according to the
 procedure in Fig.~\ref{fig:LHAE_rsacce}.}
\end{itemize}

\begin{figure*}[!htb]
\begin{center}
\fbox{
\begin{minipage}[t]{0.42\textwidth}
\begin{tabular}[t]{l}
 $\Encrypt(\pi^p_{i,\ell},m_0,m_1,\iv,H)$: \\
 $\quad C_0 \xleftarrow{\$} \SE.\Enc(k, \iv, H,m_0)$ \\
 $\quad C_1 \xleftarrow{\$} \SE.\Enc(k, \iv, H,m_1)$ \\
 $\quad \text{If } C_0 = \perp \text{ or } C_1 = \perp$ \\
 $\quad \quad \text{return } \perp$ \\
 $\quad \mathcal{C} = \mathcal{C} \cup C_b$ \\
 $\quad \text{return } C_b$ \\
\end{tabular}
\end{minipage}
\vline \quad
\begin{minipage}[t]{0.42\textwidth}
\begin{tabular}[t]{l}
 $\Decrypt(\pi^p_{i,\ell},C,\iv,H)$: \\
 $\quad \text{If } b = 1 \wedge C \not\in \mathcal{C}$ \\
 $\quad \quad \text{return } \SE.\Dec(k,\iv,H,C)$ \\
 $\quad \text{return } \perp$ \\
\end{tabular}
\end{minipage}
}
\caption{Encrypt and Decrypt oracle in the RSACCE security experiment}
 \label{fig:LHAE_rsacce}
\end{center}
\end{figure*}

%=====================================================
\subsection{Security Definition} \label{sec:sec_def}
%=====================================================

We define the security model of resumable server-only
authenticated confidential channel establishment (RSACCE).

\subsubsection{Matching Conversations}
In our SACCE protocol, a client always initiates an
instance of the protocol and a server always sends the
last message of the instance in a whole handshake.
We define matching conversations as in~\cite{JKSS12:ACCE}.
We denote by $T^p_{i,\ell}$ the transcript of
$\pi^p_{i,\ell}$, i.e., the history of all messages sent
and received by $\pi^p_{i,\ell}$ in chronological order
(not including the initialization-symbol $\top$).
For two transcripts, $T^p_{i,\ell}$ and
$T^{p^{\prime}}_{j,\ell'}$ we say that $T^p_{i,\ell}$
is a \textit{prefix} of $T^{p^{\prime}}_{j,\ell'}$ if
$T^p_{i,\ell}$ contains at least one message, and
$T^p_{i,\ell}$ is identical to
$T^{p^{\prime}}_{j,\ell'}$ except the last message sent
by $\pi^{p^{\prime}}_{j,\ell'}$.
In QUIC, there are two type keys initial key $\ik$ and
forward secure key $\key$.
We define two type Matching conversations according to
a state of the instance.

\begin{definition}[Matching conversations for initial key]
 We say that $\pi^c_{i,\ell}$ and $\pi^s_{j,\ell'}$ have
 a matching conversation for initial key with each other if
 in addition to $\ell=\ell'$,
 \begin{itemize}
  \item{Both oracles, $\pi^c_{i, \ell}$ and
  $\pi^s_{j,\ell'}$, pre-accept ($\Lambda = \preaccept$) and
  $T^c_{i,\ell} = T^s_{j,\ell'}$}
 \end{itemize}
\end{definition}
\begin{remark}
 The client reach a state $\preaccept$ before the
 server receives the message. However, the client can know whether
 a server indeed receives it since the server will send the
 last message to a client.
\end{remark}
\begin{definition}[Matching conversations for forward secure key]
 We say that $\pi^c_{i,\ell}$ and $\pi^s_{j,\ell'}$ have
 a matching conversation with each other if in addition
 to $\ell=\ell'$,
 \begin{itemize}
  \item{Both oracles, $\pi^c_{i, \ell}$ and
  $\pi^s_{j,\ell'}$, accept ($\Lambda = \accept$) and
  $T^c_{i,\ell} = T^s_{j,\ell'}$; or}

  \item{The server oracle $\pi^s_{j, \ell'}$ accepts
  ($\Lambda = \accept$),
  and $T^c_{i,\ell}$ is a prefix of $T^s_{j,\ell'}$.}
 \end{itemize}
\end{definition}
\begin{remark}
 The second condition is necessary because in our SACCE
 protocol a server accepts a session before sending the
 last message to a client and cannot know whether a
 client indeed receives it.
\end{remark}

\subsubsection{RSACCE Game}
We define the RSACCE game between an adversary $A$ and
a challenger.
In this game, the challenger firstly instantiates the
collection of oracles $\{\pi^p_{i,\ell}\}$.
Then the challenger generates the certificate's
signing/verification keys; generates long-term keys
$(\pk_s, \sk_s)$ for all servers; and issues the
certificates for all public keys.
The adversary receives all public keys $\pk_s$ with
identity $s$ as input.
Now the adversary may start by issuing $\Send$,
$\Reveal$, $\Corrupt$, $\Encrypt$ and $\Decrypt$ queries.
Finally, the adversary outputs
$(p, i, \ell, b^{\prime})$ and terminates.

\begin{definition}[Correctness]
 Assume a ``benign" adversary $A$, which picks two
 arbitrary oracles, $\pi^c_{i, \ell}$ and
 $\pi^s_{j, \ell^{\prime}}$, and performs a sequence of
 $\Send$-queries by faithfully forwarding all messages
 between $\pi^c_{i, \ell}$ and $\pi^s_{j, \ell^{\prime}}$.
 Let $\ik^c_{i, \ell}$ and $\key^c_{i, \ell}$ denote the
 key computed by $\pi^c_{i, \ell}$ and let
 $\ik^s_{j, \ell^{\prime}}$ and $\key^s_{j, \ell^{\prime}}$
 denote the key computed by $\pi^s_{j, \ell^{\prime}}$.
 We say that RSACCE protocol is \textit{correct}, if two
 arbitrary server and client oracles, $\pi^c_{i, \ell}$
 and $\pi^s_{j, \ell^{\prime}}$, always hold that:
 \begin{itemize}
  \item{Both oracles, $\pi^c_{i, \ell}$ and
  $\pi^s_{j, \ell^{\prime}}$, have
  \textit{a matching conversation} for initial key
  and forward secure key with each other; and}

  \item{Both initial keys, $\ik^c_{i, \ell}$ and
  $\ik^s_{j, \ell^{\prime}}$, are the same
  ($\ik^c_{i, \ell} = \ik^s_{j, \ell^{\prime}}$).}

  \item{Both forward-secure keys, $\key^c_{i, \ell}$ and
  $\key^s_{j, \ell^{\prime}}$, are the same
  ($\key^c_{i, \ell} = \key^s_{j, \ell^{\prime}}$).}
 \end{itemize}
\end{definition}

\subsubsection{Security Requirements}
We now define the following advantage measures.

\begin{definition}[Server Authentication] \label{def:rsacce-sa}
 $\Adv^{\rsaccesa}_{\Pi}$ (A) is the probability that when
 $A$ terminates, there is a client oracle $\pi^c_{i, \ell}$
 such that the following conditions hold:
 \begin{itemize}
  \item{If $\ell = 0$, $\pi^c_{i, 0}$ pre-accepts
  ($\Lambda = \preaccept$) when $A$ issues its
  $\tau_0$-th query with intended partner $\peer=s$, }

  \item{If $\ell = 0$, there is no server oracle
  $\pi^s_{j, 0}$ such
  that $\pi^c_{i,0}$ has a matching conversation for initial
  key with
  $\pi^s_{j,0}$ or there exist plural oracles that have
  a matching conversation for initial key with $\pi^c_{i,0}$,}

  \item{If $\ell \neq 0$, $\pi^c_{i, \ell}$
  accepts ($\Lambda = \accept$) when $A$ issues its
  $\tau_0$-th query with intended partner $\peer=s$, }

  \item{If $\ell \neq 0$, there is no server oracle
  $\pi^s_{j, \ell}$ such
  that $\pi^c_{i,\ell}$ has a matching conversation for forward
  secure key with
  $\pi^s_{j,\ell}$ or there exist plural oracles that have
  a matching conversation with $\pi^c_{i,\ell}$, and}

  \item{$\Server$ with identity number $s$ is $\tau_{s}$-corrupted with
  $\tau_0 < \tau_{s}$ and the server oracle $\pi^s_{j, \ell}$ is
  $\tau_{so}$-corrupted with $\tau_0 < \tau_{so}$. }

 \end{itemize}
 We say that protocol $\Pi$ has \textit{server authentication},
 if $\Adv^{\rsaccesa}_{\Pi}(A)$ is negligible in $\kappa$.
\end{definition}

\begin{remark}
 The \textit{server authentication} is a natural extension
 of the counter part of~\cite{KPW13:SACCE}, which implies
 that if a client accepts, protocol $\Pi$ guarantees that
 the client has a matching conversation with the intended
 parter (server). In contrast to the original
 definition~\cite{KPW13:SACCE}, we allow an adversary to
 submit $\Corrupt$ queries.
 In our definition, the fifth conditions ensure the
 consistency of the server handshake sessions.
 If the adversary can issue $\Corrupt$ query to the server
 $\Server$ with identity number $s$ or the server oracle $\pi^s_{j, \ell}$
 before $\pi^s_{j, \ell}$ reaches accept, she can
 impersonate the server because she can make valid response
 (SHLO) using long-term secret key $sk_s$ or server's
 Diffie-Hellman secret value $t_s$.
 In 0-RTT connection, the client immediately reaches pre-accept state
 after sending the first message. If the adversary drop this message, the adversary
 easily break our server authentication since there is no server oracle
 such that the client oracle has a matching conversation for initial key.

 \end{remark}

\begin{definition}[Channel Confidentiality] \label{def:rsacce-cc}
 $\Adv^{\rsaccecc}_{\Pi}$ (A) is defined to be
 $x$ - $\frac{1}{2}$ where $x$ is the probability that
 the adversary $A$ outputs $(p, i, \ell, b^{\prime})$,
 with $0\leq \ell$, such that $b = b^{\prime}$ where
 $b^{\prime} \in \bits$ is set during the
 $\Encrypt(\pi^p_{i,\ell},\dots)$ query and we define
 $b=\bot$ unless the following conditions hold:
 \begin{itemize}
  \item{$\pi^p_{i,\ell}$ pre-accepts
  ($\Lambda = \preaccept$) when $A$
  issues its $\tau_0$-th query.}

  \item{If $\pi^p_{i,\ell}$ is a client oracle, the
  intended pater $\Server$ with identity number $s$ is $\tau_s$-corrupted
  with $\tau_0 < \tau_s$ and the server oracle $\pi^s_{j,\ell}$ is
  $\tau_{so}$-corrupted with $\tau_0 < \tau_{so}$.}

  \item{If $P$ is a server $\Server$ with identity number $s$, then there
  is a client $\Client$ with identity number $c$ maintaining oracle
  $\pi^c_{j,0}$ that has a matching conversation for initial key and
  forward secure key with $\pi^s_{i,0}$.}

  \item{The adversary does not issue a $\Reveal$ query
  to either $\pi^p_{i,\ell}$, nor to
  $\pi^{p^{\prime}}_{j,\ell}$ such that $\pi^p_{i,\ell}$
  has a matching conversation with
  $\pi^{p^{\prime}}_{j,\ell}$, and client oracles $\pi^c_{i,k}$
  ($k < \ell$) is $\tau_{co}$-revealed with $\tau_0 < \tau_{co}$.}
 \end{itemize}
 We say that protocol $\Pi$ has
 \textit{channel confidentiality} if
 $\Adv^{\rsaccecc}_{\Pi}(A)$ is negligible in $\kappa$.
\end{definition}

\begin{remark}
We extend the security requirement of
\textit{channel confidentiality} of SACCE~\cite{KPW13:SACCE}.
The original security notion takes care of message
confidentiality of ciphertexts sent by a (honest)
client, only. It is because an adversary can trivially
play a role of an honest client and have a matching
conversation with a (honest) server with the same
session key. In our definition, the third condition
indicates that an adversary may send the $\Encrypt$
query to even \textit{server} $\Server$ (to break
message confidentiality of the challenge ciphertext
sent by \textit{server oracle} $\pi^s_{i,\ell}$) as
long as the initial full handshake is established
between $\Server$ with identity number $s$ and an \textit{honest} client
$\Client$ with identity number $c$ (not the adversary). Later, if the
adversary can hijack some abbreviate handshake session
and share a new session key with server $\Server$,
then it can break our channel confidentiality.
The second condition specifies forward-secrecy among
the other sessions in the
sense that message confidentiality of $\pi^p_{i,\ell}$
is preserved, as long as the adversary does not
corrupt the server's long-term secret key $sk_s$ and Diffie-Hellman
secret value $t_s$ in $\SCFG$.
The fourth condition specifies forward-secrecy among
a full handshake and abbreviate handshakes in the sense
that message confidentiality of $\pi^p_{i,\ell}$ is preserved,
as long as the adversary does not reveal the oracles.
\end{remark}

\subsubsection{RSACCE security}
We define the RSACCE security.

\begin{definition}[RSACCE secure]
 We say that the protocol $\Pi$ is RSACCE secure
 if $\Pi$ satisfies \textbf{correctness},
 \textbf{server authentication},
 \textbf{channel confidentiality}.
\end{definition}