%=====================================================
\section{Quick UDP Internet Connections} \label{sec:quic}
%=====================================================

Quick UDP Internet Connections (QUIC) is a protocol
developed by Google and this protocol is still under
development.
The concepts of QUIC are (1) to reduce connectivity
overheads before a client sends encrypted data and
(2) to obtain better security guarantee than TLS.
To realize concept (1), QUIC is not defined over
TCP but UDP, because TCP requires three-move handshake
before initiating a cryptographic handshake, but UDP
does not have. In addition, a client can send encrypted
data concurrently with CHLO which is second query of the
client.
To realize concept (2), QUIC supports only secure cipher
suites. Especially, a support algorithm of key exchange
is only ephemeral elliptic curve Diffie-Hellman.

%=====================================================
\subsection{$1$-RTT Connection Establishment} \label{sec:quic_1rtt}
%=====================================================

We provide the abstract model of 1-RTT connection establishment
for the initial key in Fig.\ref{fig:quic_abst_1rtt_init} and
the final key in Fig.\ref{fig:quic_abst_1rtt_last}.
%
\input{04_z1_protocol_1rtt_overview}
\ONERTTtrue
\ORIGINALtrue
\input{04_z2_forward_secure_key}
%
A server generate server config $\SCFG$ before a request from a client.
We describe the detail of generation of $\SCFG$ in section \ref{sec:proposed_scheme}.
SCFG is composed of seven parameters AEAD, SCID, PDMD,
PUBS, KEXS, and OBIT, and EXPY. The important parameters
are SCID which is an opaque 16 byte identifier for
this server config, PUBS which is server's
Diffie-Hellman public value, and EXPY which is expiry time
for this server config. The details of other parameters
are described in~\cite{QUIC:Crypto}.
Our definition considers only important parameters.
Firstly, the client sends an inchoate client
hello ($m_1$) to start the connection.
The client needs $\STK$ to make a server pre-accept and share
a session key since the server require the $\STK$ to the client
when the server calculates initial key $\ik$ or final key $\key$.
After the server receives inchoate client hello, it
sends a rejection ($m_2$). The rejection ($m_2$) contains
source address token (STK), server config ($\SCFG$) which
include a signature $\sigma_s$ of the server config generated
by the server long term secret key $sk_s$. The client uses
STK in future queries to demonstrate ownership of their
source IP address.
The client can calculates the initial key after receiving
a rejection ($m_2$). Before this calculation, the client
checks the server config $\SCFG$ and generate $\NONC$ which consists
of a random value, and ephemeral
Diffie-Hellman values $t_c$.
The client sends a client hello ($m_3$) to the server.
After the server receives a client hello ($m_3$), the
server check this query. $\STK$ is an opaque byte string
from the client's point of view. From the server's point
of view it's an authenticated-encryption block that
contains, at least, the client's IP address and a time
stamp by the server. The server decrypt $\STK$ and
validate time and source IP address.
The client and server
exchange data encrypted and authenticated using authenticated
symmetric encryption $\SE$ with the initial key $\ik$ after
sharing the initial key $\ik$.
The server send a server hello ($m_4$) which contains
a ciphertext which consists of a new $\STK$ and ephemeral server's
Diffie-Hellman public value after exchanging data and
calculate the final key $\key$.
The client validate a server hello ($m_4$) and calculate
the final key $\key$ and cache the data.

%=====================================================
\subsection{$0$-RTT Connection Establishment} \label{sec:quic_0rtt}
%=====================================================

We provide the abstract model of QUIC for 0-RTT in
Fig.\ref{fig:quic_abst_0rtt}.

%
\input{04_z3_protocol_0rtt_overview}
%
Firstly, the client sends a client hello using cache data.
The server searches $\SCFG$ with $\SCID$ and validate a
client hello.
After the client sends a client hello or the server validate
a client hello, they calculate the initial key $\ik$.
The flow for the final key $\key$ is the same as
1-RTT case.


%=====================================================
\subsection{Security Concerns About QUIC} \label{sec:quic_detail}
%=====================================================
In \cite{LJBN15:QUIC}, Lychev et al.~showed that QUIC is secure in the QACCE security model.
However, they also reported the following attacks:
(1) the server config replay attack, 
(2) the source-address token replay attack,
(3) the connection ID manipulation attack,
(4) the source-address token manipulation attack, and 
(5) the crypto stream offset attack. 


These attacks make it easy that an adversary executes the Distributed Denial of Service
(DDoS) attacks. 
In this paper, we do not consider the attack (5) because it is irrelevant to handshake connections.

The attacks, (1), (3), and (4), are a kind of the man-in-the-middle attacks, where  
an adversary is positioned on the path between the client and the server and 
makes inconsistent views to a client and a server. 
In the current version of QUIC, the client cannot be aware of some kind of change of 
$\SCFG_{pub}$, $\cid$, and $\STK$. 
(Indeed, the adversary can freely modify
$\STK$ and $\cid$ because there is no way that  the client can recognize it.
On one hand, $\SCFG_{pub}$ has the server's signature, but 
$\SCFG_{pub}$ is independent of the client's first query. So, the client cannot recognize it even if 
$\SCFG_{pub}$ is collected by the adversary when it eavesdrop another connection with the same server.)
After the adversary makes inconsistent views to the client and the server, 
they cannot share the same key. 
So, all encrypted data the (honest) client sends to the server cannot be decrypted correctly by the server.  
However, since the client does not recognize it, he might send encrypted data again and again and 
would increase the server's load. 
  
We remark that these attacks do not work in our RSACCE security model, because of 
the server authentication. 
When a party accepts or pre-accepts,  there exists a unique matching conversation with another side party 
and the client and the server should share the same key. 

The attack  (2) is a hijacking attack. First, an adversary sees a full handshake connection.
Then, the adversary successfully establishes a $0$-RTT abbreviate connection with the server, 
instead of the initial client. 
In the current version of QUIC, this attack is unavoidable (if the adversary can be positioned on the path), 
because the adversary can collect $T_s$, $\SCID$, and $\STK$ from the initial full handshake connection. 
We note that \textit{source-address token} $\STK$ is an authenticated encryption block issued by the server, 
which contains at lease the client's IP address and the server's time stamp. 
when he receives it from the client, the sever decrypts it and checks the contents.
Therefore, to succeed this attack, the adversary can be positioned on the path between the client and the server.  

This attack does not work in our RSACCE security model, due to the channel binding.
The channel binding guarantees that an adversary cannot convince the server if he is not the same client in 
the initial full handshake connection.

\if0
An adversary first collect a copy of the target server's 
$\SCFG_{pub}$. It is possible for the adversary either to actively start a full $1$-RTT QUIC handshake connection with the server or to passively see any full handshake connection with the server. 
Once he has $\SCFG_{pub}$, he waits for the target client to start a connection. 
Then, when he see the first message from the client, he respond with the collected $\SCFG_{pub}$ 
as if it comes from the real server, before the server sends back with the proper one.
\fi

\if0
For more details about (1), (3) and (4), the adversary can forge
$\STK$ and $\cid$ because there are no authentication mechanism
for these parameters.
The server generate signature for $\SCFG$, however, the generation
of $\SCFG$ is independent from client's first query and these parameters
which generated at client's first query
are not certificated and even authenticated.
If the adversary forge these parameters, the client and server cannot
detect it.

For more details about (2), although QUIC has a mechanism to prevent forgery,
whose mechanisms is called \textit{source-address token}
(see below), the adversary can forge an abbreviate handshake
query as follows: An adversary can obtain $\SCID$ and $\STK$ from $\REJ$
response, which is the first response from a server oracle.
Then, the adversary make $(\overline{T}_c^{\prime},
\overline{\NONC}^{\prime}, \overline{\cid})$ and send $(\overline{T}_c^{\prime},
\SCID, \overline{\NONC}^{\prime}, \STK, \overline{\cid})$ to the server after a
full handshake between the server and its intended partner
is established.
The server cannot distinguish whether the query in an abbreviate handshake
comes from the intended partner or not. Because there is no
authentication mechanism for this query. The server accepts
this query and calculates the session keys with the value
of the adversary.

If the protocol satisfies RSACCE secure, the protocol prevents these attacks (1)~(4).
\fi
\subsubsection{More about Source Address Token} \label{sec:source_address_token}
Source-address token ($\STK$) is introduced to QUIC in order to
prevent IP address spoofing.
A server generates a new $\STK$ every time he sends a
message to a client.
The client updates $\STK$ when the client receives a new one from
the server and sends it back along with his message.
$\STK$ is an opaque byte string from the client's point of view.
From the server's point of view it's an authenticated-encryption
block that contains, at least, the client's IP address and the time
stamp issued by the server.
\if0
$\STK$ is encrypted except for the first server's query ($\REJ$).
However, in our model the adversary has full control over the
communication network and hence it can obtain $\STK$ and use it to
forge a future query.
\fi