%=====================================================
\section{Our proposed scheme} \label{sec:proposed_scheme}
%=====================================================

We note that QUIC is not RSACCE secure.
We propose a new scheme which satisfy RSACCE secure and
reduce interactions.

%=====================================================
\subsection{1-RTT Connection Establishment} \label{sec:quic_prop_1rtt}
%=====================================================

The abstract model of our proposed scheme is in
Fig.~\ref{fig:quic_prop_1rtt}.

\input{05_z1_proposed_1rtt_overview}

We define three phases of our proposed scheme handshake in 1-RTT.
(1) \textbf{Initiate},
(2) \textbf{Key Agreement},
(3) \textbf{Data Exchange}.
The flow of (1), (3) are the same as the same as the original QUIC
handshake in 1-RTT.

\input{05_prop_01_02_key_agr}

%=====================================================
\subsection{0-RTT Connection Establishment} \label{sec:quic_prop_0rtt}
%=====================================================

The abstract model of our proposed scheme is in
Fig.~\ref{fig:quic_prop_0rtt}.

\input{05_z2_proposed_0rtt_overview}

We define four phases of our proposed scheme handshake in 0-RTT.
(1) \textbf{Initial Key Agreement},
(2) \textbf{Initial Data Exchange},
(3) \textbf{Key Agreement}, and
(4) \textbf{Data Exchange}.
The flow of (2), (3), (4) are the same as the 1-RTT
handshake.
\input{05_z2_proposed_operations}

%=====================================================
\subsection{Security of our proposed scheme} \label{sec:quic_proof}
%=====================================================

\begin{theorem} \label{theorem:proposed_scheme}
 Let $\mu$ be the output length of $\PRF$, let $\lambda$ be
 the length of $\SCID$, let $\nclient$ be the number of
 clients, let $\nserver$ be the number of servers, let
 $\noracle$ be the number of oracles of each parties, and
 let $n_{\ell}$ be the maximum number of resumptions. Assume
 that the $\PRF$ is $(t, \epsilon_{\prf})$-pseudo-random
 function family, the signature shceme
 $\SIG$ is $(t, \epsilon_{\sig})$-secure against existentially
 unforgeable under adaptive chosen-message attacks, the DDH
 problem on $G$ is $(t, \epsilon_{\ddh})$-hard, the hash
 function family $\mathcal{H}$ is
 $(t,\epsilon_{H})$-collision-resistant (CR), the symmetric
 authenticated encryption scheme $\SE$ is
 $(t, \epsilon_{\sLHAE})$-secure.
 Then for all PPT adversaries, our proposed scheme is RSACCE secure.
\end{theorem}

Our proposed scheme can prevent the five attacks in~\cite{LJBN15:QUIC}.

\begin{itemize}
 \item{Server Config Replay Attack}
  In this attack, the adversary collect
 \item{Source-Address Token Replay Attack}
 \item{Connection ID Manipulation Attack}
 \item{Source-Address Token Manipulation Attack}
 \item{Crypto Stream Offset Attack}
\end{itemize}

We prove Theorem~\ref{theorem:proposed_scheme} by proving two lemmas.

\begin{lemma} \label{lemma:proposed_scheme_rsacce-sa}
 $\Adv^{\rsaccesa}_{P}(A)$ is at most
 \begin{equation}
  \Adv^{\rsaccesa}_{P}(A) \leq \frac{n_s n_c}{2^{\lambda}} m_s \epsilon_{\sig}
 \end{equation}
\end{lemma}
%
\input{05_z3_proposed_scheme_sa}

\begin{lemma} \label{lemma:proposed_scheme_rsacce-cc}
 $\Adv^{\rsaccecc}_{P}(A)$ is at most
 \begin{equation}
  \Adv^{\rsaccecc}_{P}(A) \leq \Adv^{\rsaccesa}_{P}(A) + n_sn_c\ell(\epsilon_{\ddh} + 2\epsilon_{\prf} + 2\epsilon_{\sLHAE})
 \end{equation}
\end{lemma}
%
\input{05_z4_proposed_scheme_cc}